Differentiable Optics with {\Large $\partial$}Lux: I - Deep Calibration of Flat Field and Phase with Automatic Differentiation

### 2022-11-10 src/tex/ms.tex
[showyourwork] overleaf sync

% Define document class
\documentclass[]{spie}
\usepackage[utf8]{inputenc}
\usepackage{showyourwork}
\usepackage{xspace}
%\documentclass[a4paper]{spie}  %>>> use this instead for A4 paper
%\documentclass[nocompress]{spie}  %>>> to avoid compression of citations

\renewcommand{\baselinestretch}{1.0} % Change to 1.65 for double spacing
\usepackage{amsmath,amsfonts,amssymb}
\usepackage{graphicx}
\usepackage[colorlinks=true, allcolors=blue]{hyperref}

\usepackage{relsize}

@@

In this series of papers, we present a new software package, \dlux, for fitting high-dimensional parametrized physical optics models to astronomical data. By using the Python library \textsc{Jax}\cite{jax}, we obtain \ac{gpu} hardware acceleration, as well as automatic differentiation\cite{Margossian2018} features that enable high dimensional optimization and inference with gradient descent or \ac{hmc}. In the present paper, we focus on the particular problem of estimating the \ac{prf} and \ac{psf} simultaneously - i.e. joint flat field calibration and phase retrieval. In Paper II, we will show how automatic differentiation enables improvements to hardware \textit{design}, directly calculating and optimizing the Fisher information and therefore fundamental figures of merit of an optical system end-to-end.

@@

\section{\dlux Differentiable Optical Models}
\label{sec:dlux}

% Physical Optics Forwards Models
% poppy/WebbPSF
% Autodiff
% Review backprop/NNs
% Jax, PyTorch, Julia
% Autodiff Optics
% WaveBlocks
% Sitzmann etc
% Liaudat
% Morphine
% Overview of Wong et al 2021
% dLux
% Equinox
% Features
% Example of how to set up a model from layers

>>>>

% Define document class
\documentclass[twocolumn]{spie}
% \documentclass[twocolumn]{aastex631}
\usepackage[utf8]{inputenc}
\usepackage{showyourwork}
\usepackage{xspace}
%\documentclass[a4paper]{spie}  %>>> use this instead for A4 paper
%\documentclass[nocompress]{spie}  %>>> to avoid compression of citations

\renewcommand{\baselinestretch}{1.0} % Change to 1.65 for double spacing
\usepackage{amsmath,amsfonts,amssymb}
\usepackage{graphicx}
% \usepackage[colorlinks=true, allcolors=blue]{hyperref}

@@

In this series of papers, we present a new software package, \dlux, for fitting high-dimensional parametrized physical optics models to astronomical data. By using the Python library \textsc{Jax}\cite{jax}, we obtain \ac{gpu} hardware acceleration, as well as automatic differentiation\cite{Margossian2018} features that enable high dimensional optimization and inference with gradient descent or \ac{hmc}. In the present paper, we focus on the particular problem of estimating the \ac{prf} and \ac{psf} simultaneously - i.e. joint flat field calibration and phase retrieval. In Paper II, we will show how automatic differentiation enables improvements to hardware \textit{design}, directly calculating and optimizing the Fisher information and therefore fundamental figures of merit of an optical system end-to-end. We make \dlux available as open-source software on GitHub\footnote{\href{https://github.com/LouisDesdoigts/dLux}{github.com/LouisDesdoigts/dLux}}, and encourage interested readers to use and contribute to this package as a community resource. This paper has been compiled using ShowYourWork \cite{Luger2021}, so that all figures link to the code used to produce them.

@@

\section{\dlux Differentiable Optical Models}
\label{sec:dlux}
\textcolor{red}{Louis - this is your bit to write!}
% Physical Optics Forwards Models
% poppy/WebbPSF
% Autodiff
% Review backprop/NNs
% Jax, PyTorch, Julia
% Autodiff Optics
% WaveBlocks
% Sitzmann etc
% Liaudat
% Morphine
% Overview of Wong et al 2021
% dLux
% Equinox
% Features
% Example of how to set up a model from layers
